Verifying the \shaThree\ Implementation from \openssl\ with the Software Analysis Workbench

### 2022-01-07 paper/abstract.tex
Add minor revisions

\shaThree\ is the new standard from \nist\ for computing digests. 
\openssl\ is one of the most widely used implementations of cryptographic protocols.
\cryptol\ and the Software Analysis Workbench (\saw) are a language and verification engine to specify cryptographic primitives and prove equivalence to implementations.
As digests are the basis for all cryptographic protocols, the research in this paper is an automated \saw\ proof of equivalence between the \shaThree\ standard and the actual \openssl\ implementation in C.
The research contributes \cryptol\ specifications for the published standard and the \openssl\ implementation of the standard with its several changes.
The equivalence proof shows the importance of overrides in \saw\ to replace C code with \cryptol\ to reduce the complexity of the proof obligations that must be accomplished relative to the implementation in C.
The research establishes the viability of verifying modern cryptographic primitives and the importance of modularity in their definitions, and implementations, for overrides.

>>>>

\shaThree\ is the new standard from \nist\ for computing digests. 
\openssl\ is one of the most widely used implementations of cryptographic protocols.
\cryptol\ and the Software Analysis Workbench (\saw) are a language and verification engine to specify cryptographic primitives and prove equivalence to implementations.
As digests are the basis for all cryptographic protocols, the research in this paper is an automated \saw\ proof of equivalence between the \shaThree\ standard and the actual \openssl\ implementation in C.
The research contributes \cryptol\ specifications for the published standard and the \openssl\ implementation of the standard with its several changes.
The equivalence proof shows the importance of overrides in \saw\ that replace C code with \cryptol\ to reduce the complexity of the proof obligations that must be accomplished relative to the implementation in C.
The research establishes the viability of verifying modern cryptographic primitives and the importance of modularity in their definitions, and implementations, for overrides.
